\begin{abstract}
We apply a single uniform protocol to the four canonical economic
cycles (Kitchin 3--5 years, Juglar 7--11 years, Kuznets 15--25
years, Kondratieff 40--60 years) across five independent
macroeconomic panels spanning 1700--2024
(Bank of England Millennium, J\`ord\`a-Schularick-Taylor R6, World
Bank annual aggregates, FRED/Eurostat/OECD/BIS quarterly, sectoral
historical). The protocol is dual-null: AR(1) bootstrap as the
primary existence test, ARFIMA(0,\(\hat d\),0) as the long-memory
robustness check, plus per-cell ADF, KPSS, GPH \(\hat d\) and DFA
Hurst diagnostics, band-edge sensitivity tests at \(\pm 1\)y, and
rolling-window verdicts at 50--80y. On a (panel, group, variable,
cycle) grid of more than 1\,400 testable cells we find three
substantive concentrations, one reinforced recast, and one
displaced artefact. Juglar is empirically alive on investment
and unemployment across the J\`ord\`a-Schularick-Taylor advanced
economies (2.2-fold excess over null on 605 cells); the UK
unemployment cell on BoE Millennium survives both the AR(1) and
the ARFIMA(0, \(\hat d=0.49\), 0) null
(\(p_{1,\mathrm{AR(1)}}=0.004\),
\(p_{1,\mathrm{ARFIMA}}=0.002\)). Kuznets passes on house prices
(46\,\% of testable JST countries), on population and on credit
aggregates (1.9-fold excess). Kitchin passes on emerging-market
credit aggregates on the quarterly BIS panel (5.3-fold excess on
93 cells); the BoE Kitchin cell, by contrast, fails our R4
band-sensitivity test (pass-rate 0\,\% under a one-year tightening
of the lower edge) and is no longer treated as supporting
evidence. The 40--60y band passes only on UK debt series on the
Bank of England Millennium panel (public-sector debt
\(p_{1,\mathrm{AR(1)}}=0.002\), \(p_{1,\mathrm{ARFIMA}}=0.022\)
at \(\hat d=+0.44\); central-government gross debt
\(p_{1,\mathrm{AR(1)}}=0.032\), \(p_{1,\mathrm{ARFIMA}}=0.048\));
we recast this finding as a \citet{reinhart_rogoff2009}
war-financing debt-chronology rather than as a vindication of
the \citet{kondratieff1925} endogenous-long-wave hypothesis,
because \emph{all} other Kondratieff-eligible UK macro series
(real GDP, CPI, real wages, share prices, population) fail
Gate~1 on both nulls. What our protocol \emph{rejects} is the
strong universalist reading: no single canonical period
describes \emph{all} macroeconomic variables across heterogeneous
panels, and the variable-specific concentrations do not survive
a strict Benjamini-Hochberg false-discovery-rate adjustment on
the joint grid at our surrogate counts. Long-memory diagnostics
show that 97--100\,\% of cells exhibit \(|\hat d|>0.1\); the
AR(1) null is therefore mis-specified on the raw level series,
and the load-bearing verdict is the ARFIMA-conditional one
where it differs. The negative result is properly scoped to the
universalist sinusoidal-on-everything reading; the positive
result vindicates the substantive theory of three canonical
cycles on the variables originally claimed, with the BoE
debt-chronology reading reinforced by long-memory-aware testing.
\end{abstract}
