\section{Introduction}
\label{sec:intro}

A century after \citet{kitchin1923}, \citet{juglar1862},
\citet{kuznets1930} and \citet{kondratieff1925} introduced the
four canonical economic cycles, the empirical status of those
cycles remains contested. The standard reading in long-wave and
econophysics work
\citep{perez2002,modelski1987,korotayev_tsirel2010} is
universalist: a single canonical period at the heart of every
macroeconomic time series. The standard reading in the empirical
business-cycle literature is sceptical: \citet{burns_mitchell1946}
refused to commit to any canonical period;
\citet{garvy1943,solomou1987,romer1999,stock_watson2003,wen2005}
have argued in turn that no canonical periodicity is universal,
and that what looks like Kondratieff, Kuznets, Juglar or Kitchin
on composite aggregates often does not appear on the underlying
variables. The two readings have rarely been confronted on the
same data through the same protocol.

This paper provides that confrontation. We apply a single
falsifiable protocol---three gates and a per-variable
safeguard---to every cell of the
\(\{\text{cycle}\}\times\{\text{panel}\}\times\{\text{country / aggregate}\}\times\{\text{variable}\}\)
grid across five independent panels spanning 1700--2024, with
threshold values committed to a public Git history before the
panels were ingested.

\paragraph{Headline finding.}
The empirical answer that emerges is more nuanced than either
extreme reading admits. The canonical cycles are alive on exactly
the variables the substantive literature predicts:

\begin{itemize}
\item the \textbf{Juglar band} passes Gate~1 on
  \textbf{investment-to-GDP and unemployment} on the JST R6
  advanced economies (2.2-fold excess on 605 testable cells),
  and on the quarterly G7Q/OECDQ unemployment aggregates
  (4.3-fold excess on 55 cells); the BoE Millennium UK
  unemployment cell survives both the AR(1) and the
  ARFIMA(0, \(\hat d=0.49\), 0) nulls
  (\(p_{1,\mathrm{AR(1)}}=0.004\),
  \(p_{1,\mathrm{ARFIMA}}=0.002\));
\item the \textbf{Kuznets band} passes on the
  \textbf{house-price index in 6 of 13 testable JST countries
  (46\,\%)}, on population (39\,\%) and on credit aggregates
  (41\,\%, 1.9-fold excess on 529 cells); on BoE, the
  real-effective and nominal-effective exchange-rate indices
  pass both nulls;
\item the \textbf{Kitchin band} passes on the \textbf{BIS
  emerging-market credit aggregates} (credit-to-GDP gap and
  ratio, household and business credit, real property prices) on
  Korea, China, Mexico, South Africa, Turkey, Russia, Indonesia
  (5.3-fold excess on 93 cells), and on the BRICS / WLD / LMC
  trade and inflation composites on the WB annual panel; the
  BoE Kitchin cell, by contrast, fails the R4 band-sensitivity
  test (pass-rate 0\,\% under a one-year tightening of the
  lower edge) and is no longer treated as supporting evidence;
\item the \textbf{40--60y band} passes on \textbf{two UK debt
  series only} (BoE Millennium 1700--2016: public-sector debt
  \(p_{1,\mathrm{AR(1)}}=0.002\),
  \(p_{1,\mathrm{ARFIMA}}=0.022\) at \(\hat d=+0.44\);
  central-government gross debt
  \(p_{1,\mathrm{AR(1)}}=0.032\),
  \(p_{1,\mathrm{ARFIMA}}=0.048\)), and on no other BoE
  variable. We recast this finding as the
  \citet{reinhart_rogoff2009} war-financing debt-chronology
  rather than as a Kondratieff vindication; the long-memory-
  aware ARFIMA null reinforces rather than overturns this
  reading (Section~\ref{sec:kondratieff_results}).
\end{itemize}

\paragraph{What we therefore claim, and what we do not.}
We claim that the substantive theory of \emph{three} canonical
cycles is empirically alive: Juglar on investment-financed
business cycles \citep{schumpeter1939,juglar1862}, Kuznets on
long swings in demographics and construction \citep{kuznets1930},
Kitchin on inventory and financial cycles
\citep{kitchin1923,metzler1941,wen2005,borio2014}. On the
40--60y band we claim only a single statistical pass on UK
public debt/GDP, and we read it as a
\citet{reinhart_rogoff2009} war-financing chronology rather
than as a vindication of the \citet{kondratieff1925}
endogenous-long-wave hypothesis: every other Kondratieff-
eligible UK macro variable fails Gate~1. We do \emph{not} claim
that any single canonical period applies universally to every
macroeconomic variable, and we do not claim that the joint
collection of unadjusted positives survives Benjamini-Hochberg
adjustment at FDR 0.05 on the full grid at our surrogate counts
(it does not). The negative result is properly scoped to the
strong universalist sinusoidal-on-everything reading; the
positive result vindicates the substantive theory of Juglar,
Kuznets and Kitchin on the named channels and recasts the
40--60y signal as a debt-financing chronology.

\paragraph{The protocol.}
Three gates cascade. Gate~1 (existence) requires the empirical
band-power inside the canonical band to exceed an
\(\AR{1}\)-bootstrap null at \(\alpha=0.05\), with a
complementary ARFIMA(0, \(\hat d_{\mathrm{GPH}}\), 0)
\citep{granger_joyeux1980,hosking1981,baillie1996} null reported
alongside to ensure that the AR(1) verdict is not an artefact
of long memory on broadband fractionally-integrated series;
per-cell ADF \citep{dickey_fuller1979}, KPSS \citep{kpss1992},
GPH \(\hat d\) \citep{geweke_porter_hudak1983} and DFA Hurst
\(\hat H\) \citep{peng1994} diagnostics are recorded
(Section~\ref{sec:methods}). A phase-coherence diagnostic
\citep{theiler_et_al1992,schreiber_schmitz2000} is reported but
is degenerate by Parseval against band-power and does not gate
the verdict. Gate~2 (consensus) requires agreement of at least
three of four heterogeneous estimators (Christiano-Fitzgerald,
Morlet, Hamilton-switching, PELT). Gate~3 (cross-aggregate
concordance) counts how many of the World Bank
income-stratified aggregates agree, without treating asymmetric
outcomes as failure (this is not a universality test by
construction: Section~\ref{sec:criteria}). A per-variable
safeguard \citep{wen2005} filters composite-aggregation
artefacts. Two further robustness checks ship with the
protocol: a band-edge sensitivity test at \(\pm 1\)y for
Kitchin/Juglar and \(\pm 2\)y for Kuznets/Kondratieff, and a
rolling-window Gate~1 at 50--80y windows with 25--40y step, both
reported in Appendix~\ref{app:per_variable}.

\paragraph{Calibration.}
The empirical power of the protocol is well-mapped. On
AR(1)+cosine alternatives at \(\mathrm{SNR}\geq 0.3\), Gate~1
detects 100\,\% of cycles
(Appendix~\ref{app:methods}). On Markov-switching and
multifractal alternatives the power is lower (3--26\% across SNR)
and we discuss the implications: the protocol's verdict is
properly scoped to the linear-sinusoidal reading of each
canonical cycle, which is precisely what the original
historical claims made.

\paragraph{Commitment of thresholds (``threshold transparency'',
not pre-registration).}
The cycle bands, surrogate counts, gate thresholds and
aggregate groupings were committed to the project's public Git
history before any panel was ingested. We use the term
\emph{threshold transparency} for this commitment and reserve
the term \emph{pre-registration} for the formal OSF / AEA RCT
Registry sense, which we do \emph{not} claim: those registries
require submission of a complete analysis plan to a
third-party registrar that timestamps the document outside the
researcher's control; our Git tags do not. The distinction is
recorded in Appendix~\ref{app:criteria}. The threshold values
themselves are anchored to the prior empirical literature, not
derived from the data analysed here. As a forward commitment,
we plan to register an out-of-sample replication protocol on
the OSF before any post-2024 data update is ingested, so that
future extensions are pre-registered in the formal sense even
though the present analysis is not.

The paper is short because its findings are precise.
Section~\ref{sec:data} documents the data and provenance.
Section~\ref{sec:methods} reviews the cycle-fitting arsenal.
Section~\ref{sec:criteria} formalises the gates.
Section~\ref{sec:results} reports the verdict in detail,
cycle by cycle, with all numbers backed by reproducible
empirical runs (\path{scripts/} and \path{reports/} in the
project repository). Section~\ref{sec:pointers} sketches the
alternative empirical signatures
that companion work develops as a complement to (not a
substitute for) the canonical reading.
Section~\ref{sec:conclusion} concludes.
Appendices~\ref{app:data} through~\ref{app:per_variable}
carry the technical detail.
