\section{Data}
\label{sec:data}

A central concern of any cycle-falsification claim is data quality:
weak rejection of a cycle on a short or noisy series proves little.
We therefore assemble six heterogeneous panels, each independently
sourced and each long enough to host several full periods of the
longest cycle under test (Kondratieff, 40--60y). Cross-panel
agreement and cross-source consistency over overlapping windows
are explicit gates of the protocol (Section~\ref{sec:criteria}).
Appendix~\ref{app:data} lists every variable with source URL,
licence, access date and SHA-256 checksum, and documents
pre-processing decisions (deflation, log-difference, splicing,
gap-filling).

\subsection{Five panels, 1700--2024}

Table~\ref{tab:panels} summarises the five panels. Three observations
are worth highlighting.

\begin{table*}[t]
\centering
\caption{The five macroeconomic panels used in this study. Each
panel is independent in source and methodology; cross-panel agreement
on a cycle is therefore informative. Full provenance with checksums
and licences appears in Appendix~\ref{app:data}.}
\label{tab:panels}
\small
\begin{tabularx}{\textwidth}{@{}l l l X X@{}}
\toprule
\textbf{Panel} & \textbf{Window} & \textbf{Frequency} & \textbf{Variables} & \textbf{Source} \\
\midrule
WB        & 1960--2024 & annual    & GDP, credit, CPI, etc.\ (45)            & \citet{wb_wdi} \\
Quarterly & 1970--2024 & quarterly & GDP, CPI, yields, credit, HPI (15)      & \citet{bis_credit}; \citet{fred}; Eurostat; OECD \\
JST R6    & 1870--2020 & annual    & 45 macro \& financial vars., 18 econ.\  & \citet{jorda_schularick_taylor2017} \\
BoE Mill. & 1700--2016 & annual    & UK macro \& financial (130)             & \citet{boe_millennium} \\
Sectoral  & 1700--2020 & annual    & Rail freight, pig iron, etc.\ (11)      & FRED + BEIS + OWID \\
\bottomrule
\end{tabularx}
\end{table*}

\paragraph{Coverage of the longest band.}
The Kondratieff band (40--60y) requires at least \(\approx 2.5\) full
periods for a Gate~1 dual-null test to have meaningful power
\citep{torrence_compo1998}. Only the Bank of England Millennium panel
(316y of annual UK data) and the Jord\`a-Schularick-Taylor R6 panel
(150y, eighteen advanced economies) provide that coverage. Both are
included precisely so that a critic cannot dismiss a Kondratieff
rejection as sample-size driven.

\paragraph{Frequency for the shortest band.}
The Kitchin band (3--5y) is borderline Nyquist on annual data: a
3-year period maps to a frequency of \(0.333\,\mathrm{y}^{-1}\), within
a factor 1.5 of the annual Nyquist limit. We therefore include a
quarterly panel (Q, 1995--2024) so that the Kitchin band can be tested
at \(4\times\) finer resolution.

\paragraph{Composites versus components.}
The empirical literature contains a recurring artefact whereby a
composite aggregate exhibits a cycle that none of its component
variables exhibits individually \citep{wen2005}. Our protocol enforces
a per-variable safeguard (Section~\ref{sec:criteria}) and the
sectoral panel exists precisely to test cycles on raw, unaggregated
historical series (rail freight, pig iron, cotton, wheat, etc.).

\subsection{Variables tested, variables excluded}
\label{sec:variable_selection}

The risk of a circular ``vindication'' is that we test only
variables already known from the canonical literature, then
report that the cycles appear on those variables. We address this
in two ways.

\paragraph{Pre-registered variable list, not curated for cycles.}
Each panel's variable list is the \emph{full} set shipped by the
upstream provider after the deduplication and recoding rules
documented in Appendix~\ref{app:data} (130 BoE series, 45 JST
series, 45 WB indicators, 15 quarterly variables, 11 sectoral).
The list was fixed before the Gate~1 runs and was not pruned to
remove variables that failed---this is why
Section~\ref{sec:results} reports both substantive concentrations
\emph{and} large variable subsets with null effects (e.g.\ all
ten BoE Kondratieff cells except UK debt/GDP). A reader can
recover the full per-variable evidence in
Appendix~\ref{app:per_variable}; nothing is hidden between
report and provider.

\paragraph{Variables not tested, and why.}
A small number of variables that one might expect on theoretical
grounds are absent. Total factor productivity (TFP) is not
included on the JST R6 or BoE Millennium panels because
historical TFP series before 1950 require imputation of capital
stock and labour-quality adjustments that are themselves the
output of cycle-aware decomposition methods; including them
would risk a circular construction. The term-spread on long
sovereign yields is implicit in the level series we do include
(\texttt{LH\_LTRATE} and \texttt{LH\_STIR} on JST; Consols
yield and Bank Rate on BoE) and we leave the explicit spread to
future work. Labour-force participation rates are not included
because pre-1900 series are imputed from union membership and
are not directly comparable across countries. Money velocity is
implicit in the M-aggregate and GDP series we include. These
omissions are recorded so a critic can reproduce them or
challenge them rather than guess at them.

\paragraph{A theoretical false positive must be possible.}
For the variable-specific vindication claim to be informative,
some variables that pass Gate~1 must lack a substantive
theoretical motivation for their passage---otherwise the claim
collapses into tautology. We flag one such case explicitly in
Section~\ref{sec:juglar_results}: \texttt{LH\_XRUSD} (bilateral
USD exchange rate) passes the Juglar band on 61\,\% of JST
countries but has no direct role in Juglar's
investment-and-credit mechanism. We retain the cell in the
unadjusted count but exclude it from the substantive
vindication. The protocol therefore admits theoretical
false-positives as a category, not just statistical ones.

\subsection{Reproducibility}
\label{sec:repro}

Every raw payload is fingerprinted with SHA-256 and stored in the
project SQLite catalogue (\path{ecowave/db.py:raw_files}). The full
ingestion pipeline runs end-to-end in a Docker container in
\(\approx 30\) minutes and emits JSON sidecars conforming to a
versioned schema. Appendix~\ref{app:data} reports cross-source
consistency on overlapping windows (JST vs.\ BoE on UK 1870--2016;
BIS vs.\ JST on G7 credit-to-GDP 1970--2020): pass-rates are within
the \(\pm 5\%\) tolerance committed to the project's Git
history before panel ingestion (``threshold transparency'',
Section~\ref{sec:criteria}).

\subsection{Licences and ethics}

All sources are public-domain or licensed for academic
redistribution (World Bank CC~BY~4.0; FRED public-domain; Bank of
England OBRA citation-required; JST academic-citation; BIS
citation-required). No proprietary or personally identifying data
are used. Licence texts are listed in Appendix~\ref{app:data}.
