\section{Methods: cycle-fitting and the nulls they must beat}
\label{sec:methods}

This section sketches the fitting arsenal and the null hypotheses
against which the cycles are tested. Formulae, parameter choices,
implementation references and unit-test pointers appear in
Appendix~\ref{app:methods}. The two design decisions that most
warrant explanation are the dual-null construction and the exclusion
of the Hodrick-Prescott filter; both are treated explicitly below.

\subsection{Cycle-fitting estimators}

A single cycle-detection method invites the rebuttal that the result
is an artefact of the method itself. We commit, \emph{ex ante}, to
four estimators drawn from four different families of statistical
assumption.

\paragraph{(a)~Christiano-Fitzgerald band-pass.}
The Christiano-Fitzgerald (2003) asymmetric filter
\citep{christiano_fitzgerald2003} is full-sample and optimal in
mean square for AR(1)-style processes. The instantaneous phase is
extracted via the Hilbert transform.

\paragraph{(b)~Continuous Morlet wavelet.}
The continuous wavelet transform with a Morlet mother
(\(\omega_0=6.0\), \(\Delta j=0.125\)) is the standard tool for
time-frequency localisation
\citep{torrence_compo1998,grinsted_moore_jevrejeva2004} and is used
to compute the band-power inside each canonical cycle band.

\paragraph{(c)~Markov-switching AR(1).}
Following \citet{hamilton1989}, a two-regime hidden-Markov model is
fitted by EM to the log-differenced series. A cycle is consistent
with periodic regime transitions whose dwell-time matches the
canonical band.

\paragraph{(d)~PELT changepoints.}
The PELT algorithm of \citet{killick_fearnhead_eckley2012} detects
piecewise-constant mean shifts at \(O(n)\) cost under a BIC penalty.

\paragraph{(e)~Bry-Boschan turning points.}
The procedure \citep{bry_boschan1971} revived by
\citet{harding_pagan2002} identifies peaks and troughs from a
censored local-extremum rule (minimum phase duration: five
quarters or two years), giving a deterministic, non-parametric
estimator used for cross-comparison.

Estimators (a)--(d) cast votes in the Gate~2 consensus
(Section~\ref{sec:criteria}). The four estimators are not
statistically independent: (a) and (b) both act on the
Fourier-frequency content; (c) and (d) both detect persistent
mean shifts. We treat them as four \emph{informationally diverse}
votes rather than four independent significance tests, and
quantify the residual dependence by reporting pairwise phase
agreement in Appendix~\ref{app:methods}.

\subsection{Filters and decompositions we do not use, and why}
\label{sec:methods_excluded}

\paragraph{Hodrick-Prescott filter.}
HP is excluded as a cycle-detection tool because
\citet{hamilton2018} shows that it introduces spurious cyclical
patterns even in pure random-walk data. Allowing HP into the
consensus would prejudice the test \emph{in favour} of the cycles.

\paragraph{Baxter-King band-pass.}
The Baxter-King symmetric band-pass \citep{baxter_king1999} is
weaker than Christiano-Fitzgerald at the endpoints (the most
recent and most relevant data points are dropped); we use
Christiano-Fitzgerald instead. The two filters yield band-powers
correlated above 0.95 on our panels, so the choice is not
load-bearing.

\paragraph{Unobserved-components models.}
Structural unobserved-components models of the
\citet{harvey_trimbur2003} family give an alternative path to
cycle extraction. We do not use them because they require
specifying a cyclical period as a model parameter, which would
violate the spirit of testing whether a canonical band is
present.

\paragraph{Empirical Mode Decomposition (EMD/EEMD).}
EMD suffers from mode-mixing: a single intrinsic-mode function
can absorb multiple physical frequencies, making the decomposition
non-unique and non-falsifiable in our sense.

\paragraph{Hamilton (2018) recursive filter.}
The replacement that \citet{hamilton2018} proposes for HP is, at
its core, a multi-step-ahead AR forecast residual. We include it
in Appendix~\ref{app:methods} as a robustness check on
Christiano-Fitzgerald but it does not cast an independent vote at
Gate~2.

\subsection{Null hypotheses: a dual surrogate test}
\label{sec:dual_null}

A robust assessment requires that the empirical band-power fail to
dominate \emph{both} of two surrogates drawn from different
generative families
\citep{theiler_et_al1992,schreiber_schmitz2000}. The two nulls are
\emph{not} symmetric tests of the same hypothesis; they test
different aspects of the data, and the cascade reflects this.

\paragraph{Null~1: AR(1) bootstrap.}
We fit \(y_t = \mu + \phi(y_{t-1}-\mu) + \epsilon_t\) by OLS and
simulate \(B\) independent realisations of identical length, mean,
variance and persistence (the panel-specific surrogate count is
specified in Section~\ref{sec:criteria}). The empirical band-power is
compared to the 95th percentile of the surrogate band-powers.
Null~1 directly tests \emph{cycle existence}: a band that carries
more power than a generic AR(1) process would have under random
fluctuations is evidence of cyclical structure in the standard
sense.

\paragraph{Null~2: Phase-randomised (Theiler) surrogate.}
A Fast Fourier Transform of the series yields amplitudes
\(|\hat y_k|\) and phases \(\arg\hat y_k\); we draw a new phase
sequence uniformly on \([0,2\pi)\), enforce conjugate symmetry to
keep the inverse FFT real, and invert. The phase-randomised
surrogate preserves the empirical power spectrum
\emph{exactly}---including, by construction, any cyclical band
that may already be present. Null~2 therefore does \emph{not}
test cycle existence in isolation: a series with a strong cyclical
component will have a surrogate with the same strong cyclical
component. What Null~2 tests is the \emph{temporal coherence}
inside the band: whether the phases observed in the empirical
data show structure that is not captured by their
amplitude-preserving randomisation. This distinguishes a genuine
cycle (with stable phase relationships) from a band that merely
contains power because the spectrum happens to peak there.

\paragraph{The dual criterion: existence as gate, coherence as diagnostic.}
The two nulls play asymmetric roles. The AR(1) bootstrap is the
load-bearing existence test: empirical calibration on
synthetic AR(1)+cosine alternatives (Appendix~\ref{app:methods})
shows it achieves \(\geq 80\%\) detection power above
\(\mathrm{SNR}\approx 0.2\) and saturates by
\(\mathrm{SNR}\approx 0.3\). The phase-randomised coherence
null is degenerate on simple Gaussian-linear cycles---the
spectrum-preserving surrogate carries the same band-power as
the original and a stable instantaneous frequency under
filtering---so it is non-discriminating in this regime. On
broadband non-Gaussian data it does carry information, but it
cannot be used as a primary gate. We therefore use the AR(1)
null as Gate~\ref{gate:1}, and report the phase-coherence
\(p\)-value \(p_2\) alongside as a complementary diagnostic.
This reframing follows the recommendation of
\citet{schreiber_schmitz2000} on the limits of phase-randomised
surrogates against linear test statistics, and is reflected in
the implementation (\path{ecowave/cycles/surrogate.py:dual_null}
returns both verdicts, with \texttt{reject\_cycle} set by the
AR(1) test and \texttt{reject\_existence\_and\_coherence}
provided as a conservative robustness flag).

\subsection{Anchored bands}

The cycle bands are anchored to the prior empirical literature
(not to the data analysed here) and frozen in the project's
public Git history before panel ingestion. Anchor references:
Kitchin 3--5y \citep{kitchin1923,wen2005,diebolt_doliger2008};
Juglar 7--11y \citep{juglar1862,schumpeter1939};
Kuznets 15--25y \citep{kuznets1930,korotayev_tsirel2010};
Kondratieff 40--60y \citep{kondratieff1925,modelski1987,
korotayev_tsirel2010}. We do not adjust bands \emph{post hoc} and
do not regard this as formal pre-registration in the OSF sense
(see Appendix~\ref{app:criteria}). The only frequency-related
robustness we permit is the inclusion of a quarterly panel to
mitigate Nyquist concerns on Kitchin.
