\section{Acceptance criteria: three gates and a safeguard}
\label{sec:criteria}

The protocol cascades three gates with one safeguard. The full
specification, including the limits of each criterion, is in
Appendix~\ref{app:criteria}; the gist follows.

\begin{gate}[Existence plus phase coherence]
\label{gate:1}
At significance level \(\alpha=0.05\) with \(B=1000\) surrogates,
the empirical band-power inside the canonical cycle band must
dominate the \(\AR{1}\)-bootstrap null (band-power existence)
\emph{and} the band must exhibit phase coherence beyond the
Theiler surrogate (Section~\ref{sec:dual_null}). The two surrogate
\(p\)-values are reported separately throughout
Section~\ref{sec:results}.
\end{gate}

\begin{gate}[Method consensus]
\label{gate:2}
At least three of the four estimators of Section~\ref{sec:methods}
must agree on the dominant phase at every time-point within the
panel's window. The consensus threshold is relaxed for two
specific cases that we declare in
Appendix~\ref{app:criteria}---both anchored to sampling
constraints, not to the data: two votes for Kitchin on annual
data (PELT and Bry-Boschan are under-powered below five
observations per cycle) and two votes for Kondratieff on panels
whose window is shorter than two full periods.
\end{gate}

\begin{gate}[Cross-aggregate concordance]
\label{gate:3}
Within the World Bank income-stratified family (WLD, HIC, UMC,
LMC, LIC), we count how many aggregates independently pass
Gates~\ref{gate:1}--\ref{gate:2}. A passage on four or five
aggregates is reported as ``cross-aggregate consistent''. We
explicitly do \emph{not} treat sub-five concordance as evidence
against the cycle: a cycle could be genuinely real in advanced
economies and absent in low-income ones, given different
institutional, monetary and financial structures. The verdict
distinguishes ``cross-aggregate consistent'' (5/5 or 4/5),
``advanced-economy specific'' (consistent on HIC and UMC only),
``regional'' (single-aggregate), and ``rejected'' (none).
\end{gate}

\subsection{Per-variable safeguard against compositing artefacts}
\label{sec:safeguard}

A composite aggregate can exhibit a cyclical periodicity that none
of its component variables exhibits individually, because the
aggregation smooths idiosyncratic noise into apparent coherence
\citep{wen2005}. The protocol therefore replicates Gate~\ref{gate:1}
on every input variable \emph{before} accepting a composite
result. The safeguard threshold---the fraction of component
variables that must individually pass Gate~\ref{gate:1} for the
composite to be admitted---is set at \(0.5\) following
\citet{wen2005}'s own usage on inventory data, and we report
sensitivity to the threshold (\(0.3\), \(0.5\), \(0.7\)) in
Appendix~\ref{app:per_variable}.

\subsection{Multiple-comparison correction}

The (cycle, panel, variable) grid yields on the order of
\(1\,200\) cells. We report two complementary perspectives. The
primary verdict applies the cascade as described above without
multiplicity adjustment: the cascade structure (existence,
consensus, safeguard) provides protection by construction, but
this protection rests on partial independence assumptions
between the estimators of Gate~\ref{gate:2} and between panels.
As a robustness check we report, in
Appendix~\ref{app:per_variable}, the Benjamini-Hochberg
false-discovery-rate \citep{benjamini_hochberg1995} adjusted
\(p\)-values on the full grid of Gate~\ref{gate:1} tests. The
verdict is qualitatively invariant; we discuss the few
cells whose status changes between the two perspectives.

\subsection{What ``frozen thresholds'' means here, and what it does not}

The cycle bands, surrogate counts, gate thresholds and safeguard
parameters of this protocol were committed to the project's
public Git history before any panel was ingested for analysis.
We make this commitment verifiable through dated commits and
release tags (Appendix~\ref{app:criteria}). We do \emph{not}
claim this is a formal pre-registration in the sense of the OSF
or AEA RCT registries: those registries require submission to an
independent third party before any data exploration, and our
commitment is internal to the project repository. The
distinction matters and we record it explicitly. The threshold
values themselves are anchored to the prior empirical literature
on each cycle (Appendix~\ref{app:criteria}), not derived from
the data analysed here; this is the only sense in which the
protocol is ``pre-data''.

\subsection{Falsifiability of the protocol itself}

The protocol is a conjecture and would be falsified by any of
the calibration failures listed in Appendix~\ref{app:criteria}
(synthetic AR(1) false-positive rate, embedded-cosine detection
power, textbook benchmark reproducibility for each Gate~\ref{gate:2}
estimator). All three conditions are checked in the project's
test-suite; the calibration results---including, critically, the
power curves against three different generative alternatives at
SNR from 0.2 to 2.0---are reported in
Appendix~\ref{app:methods} and discussed in
Section~\ref{sec:results}.
