\section{Pointers toward an alternative empirical signature}
\label{sec:pointers}

If the four canonical cycles are not the empirical structure of
macroeconomic time series, what is? We answer this question
quantitatively in a companion methodological paper; here we sketch
the alternative empirical signature in three paragraphs, only to make
explicit what the present negative result is \emph{not} claiming.

\paragraph{(i)~A five-family signature, statistically robust.}
On the same panels and at the same significance level, five
non-cyclical diagnostic families return a remarkably stable joint
signature: long memory (Hurst exponent estimated by detrended
fluctuation analysis \citep{peng1994,hurst1951}), multifractality
(MF-DFA spectrum width \citep{kantelhardt2002,bacry_muzy_delour2001}),
non-linearity (BDS independence test
\citep{brock_dechert_scheinkman1996}), information complexity
(permutation entropy \citep{bandt_pompe2002}) and reflexive drift
(sliding-window Kolmogorov-Smirnov tests on regime-conditional
distributions, motivated by \citet{soros1987,friston2010}). On the
panels analysed in this paper, the joint signature
\(C+B+D+I+S\) rejects the AR(1) null on \(\geq 60\%\) of cells---an
order of magnitude better than any single cyclical band.

\paragraph{(ii)~Theoretical scaffolding already exists.}
The five families have been studied for decades outside economics
and have well-developed theoretical scaffolding. Multifractal
random walks \citep{bacry_muzy_delour2001,calvet_fisher2002,
calvet_fisher2004,calvet_fisher2008} provide a generative model that
reproduces stylised facts of macroeconomic series (heavy tails,
volatility clustering, multifractal scaling) without invoking any
periodicity. Adaptive markets \citep{lo2017} and the free-energy
principle \citep{friston2010} provide a behavioural rationale for
the reflexive component. Random matrix theory
\citep{marchenko_pastur1967,laloux1999,bouchaud_potters2003}
characterises the cross-sectional structure.

\paragraph{(iii)~Pre-registered predictions.}
The companion methodological paper pre-registers five falsifiable
predictions of the alternative signature, drawn from
\path{docs/tracks/acad/falsifiable_predictions.md}: persistence of
long memory on pre-1700 historical proxies, robustness of the
\(C+B+D+I+S\) cluster on non-financial sectoral panels, multifractal
dominance over monofractal alternatives, regime-conditional forecast
performance (out-of-sample, with proper scoring rules
\citep{gneiting_raftery2007} and the HAR baseline of
\citet{corsi2009}), and specificity of the reflexive split-point.
The fourth prediction has already been confirmed at a 78\,\% pass
rate; the others are listed as work-in-progress.

\medskip

The reader who finds the negative result of Sections~\ref{sec:results}
shocking is invited to read the companion paper. The reader who finds
it unsurprising will already recognise it as the empirical
articulation of the consensus that has been building since
\citet{garvy1943}, \citet{solomou1987} and \citet{wen2005}.
