\section{Conclusion}
\label{sec:conclusion}

We applied a uniform falsifiable protocol to the four canonical
economic cycles---Kitchin, Juglar, Kuznets, Kondratieff---across
five independent macroeconomic panels spanning 1700--2024, with
threshold transparency on bands and gates, a dual AR(1) and
ARFIMA(0, \(\hat d\), 0) null at the existence gate,
per-cell long-memory and stationarity diagnostics, a
\(\pm 1\)y band-edge sensitivity test and a rolling-window
verdict at 50--80y. The finding has three halves.

\paragraph{Positive (Juglar, Kuznets, Kitchin): the canonical
cycles are alive where theory predicts.}
Three of the four canonical cycles pass Gate~1 at the
unadjusted significance level on exactly the variables the
substantive economic literature predicts. Juglar is alive on
investment-to-GDP (39\,\% of testable JST advanced economies)
and on unemployment (the quarterly panel exhibits a clean
G7Q / OECDQ / GBR / JPN unemployment signature); the BoE
Millennium UK unemployment cell passes \emph{both} the AR(1)
and the ARFIMA(0, \(\hat d=0.49\), 0) nulls
(\(p_{1,\mathrm{ARFIMA}}=0.002\)). Kuznets is alive on
house prices (46\,\% of testable JST countries), on
population (39\,\%) and on credit (41\,\%); on BoE the
real-effective and nominal-effective exchange-rate cells
also survive both nulls. Kitchin is alive on the BIS
emerging-market credit aggregates on the quarterly panel
(5.3-fold excess on 93 cells) and on emerging-market trade
and financial flows on the WB annual panel; the BoE Kitchin
cell is downgraded as a band-edge artefact under the R4
sensitivity test (pass-rate 0\,\% under a one-year tightening
of the lower edge). The positive concentrations are not
statistical noise: they cluster on the variables
\citet{kitchin1923}, \citet{juglar1862}, \citet{kuznets1930},
\citet{schumpeter1939} and \citet{borio2014} each
independently named. The substantive theory of these three
cycles is empirically vindicated on the channels each was
originally claimed to govern, with the BoE Juglar cell
specifically reinforced by long-memory-aware testing.

\paragraph{Kondratieff: not vindicated as a long wave; a UK
war-financing debt chronology, reinforced by ARFIMA.}
The Kondratieff block must be recast. Only the BoE
Millennium panel admits a meaningful test, and within it
only two UK debt series pass Gate~1: public-sector debt
(\(p_{1,\mathrm{AR(1)}}=0.002\),
\(p_{1,\mathrm{ARFIMA}}=0.022\) at \(\hat d=+0.436\)) and
central-government gross debt
(\(p_{1,\mathrm{AR(1)}}=0.032\),
\(p_{1,\mathrm{ARFIMA}}=0.048\) at \(\hat d=+0.468\));
\emph{all} other long UK series (real GDP, CPI, wholesale
prices, share prices, Bank Rate, real wages, population)
fail Gate~1 on the Kondratieff band under both nulls. The
two positive cells are consistent with
\citet{reinhart_rogoff2009}'s public-debt long wave---a
chronology of major-power conflict financing (Napoleonic,
Crimean, the two World Wars), not an endogenous economic
mechanism in the sense \citet{kondratieff1925} or
\citet{schumpeter1939} described. The R1 long-memory-aware
ARFIMA-conditional Gate~1 \emph{reinforces} rather than
overturns this reading: at the GPH-estimated \(\hat d\)
clipping bound, the headline debt-chronology cells remain
significant at \(\alpha=0.05\). The R5 rolling-window heat
map localises the strongest 40--60y power to the post-1815
Napoleonic amortisation period and to the post-1945 World
War II debt build-up---the windows the
\citet{reinhart_rogoff2009} reading anticipates. We
therefore explicitly do \emph{not} claim a Kondratieff
vindication; we claim a robust UK debt-financing
chronology, distinct from but spectrally co-located with
the 40--60y band the canonical literature labelled
``Kondratieff''. A cross-country replication with spliced
\citet{toutain1997} French debt series and other
historical debt panels would adjudicate whether the
debt-chronology reading generalises beyond the UK or
remains a colonial-empire-specific artefact.

\paragraph{Negative: the strong universalist reading fails.}
The joint collection of unadjusted positives does not survive
Benjamini-Hochberg adjustment at FDR 0.05 on the full
1\,456-cell grid at our surrogate counts. The strong
universalist sinusoidal-on-everything reading---a single
canonical period at the heart of every macroeconomic variable
on every panel---is rejected. This rejection reproduces, on a
uniform protocol with threshold transparency, the empirical
scepticism that
has been building since
\citet{garvy1943,solomou1987,romer1999,stock_watson2003,wen2005}.

\paragraph{Methodological lessons.}
Five lessons follow. First, the canonical cycles should be
read as variable-specific phenomena, not as universal
periodicities. A Juglar cycle on aggregate GDP and a Juglar
cycle on investment are two empirically different claims;
only the latter is supported by our protocol. Second, the
composite-versus-component distinction \citep{wen2005}
matters: many of the unadjusted positives on emerging-market
BIS panels arise on individual credit variables, not on
aggregate output composites. Third, the empirical power of
any cycle-detection protocol against realistic non-linear
alternatives must be reported explicitly; our protocol is
highly powerful against linear sinusoidal cycles
(\(\geq 80\%\) at \(\mathrm{SNR}\geq 0.2\) on AR(1)+cosine)
but weak against Markov-switching and multifractal
alternatives. Fourth, an AR(1) null is mis-specified on the
raw level of broadband macroeconomic series: 97--100\,\%
of cells on JST R6 and BoE Millennium return
\(|\hat d_{\mathrm{GPH}}|>0.1\) and a DFA
\(\hat H\geq 1.6\), consistent with near-unit-root
dynamics. The load-bearing existence verdict on
long-memory series is therefore the
ARFIMA(0, \(\hat d\), 0)-conditional one; pass-fail
verdicts on the AR(1) null alone are reliable only when
the ARFIMA verdict agrees. In our BoE run, sixteen cells
that pass the AR(1) null fail the ARFIMA null and should
be treated as false positives under long memory. Fifth,
band-edge sensitivity is a necessary discipline of any
cycle protocol that anchors band edges to prior empirical
literature: a substantive cycle survives a one-year
perturbation in either direction; an artefact does not.
The BoE Kitchin cell is the example of an artefact in our
panel.

\paragraph{Implications for empirical practice.}
A practitioner who wishes to model the Juglar cycle should
build on investment-to-GDP and unemployment, not on real GDP
composites. A practitioner modelling the Kuznets swing should
build on house prices, population and mortgage credit. A
practitioner modelling the Kitchin cycle on emerging markets
should build on the BIS credit aggregates. These are precisely
the channels the substantive macroeconomic literature has been
recommending; our contribution is to put the empirical map on
a uniform falsifiable protocol that can be reproduced and
revised.

\paragraph{Status of the companion paper.}
The present paper is intended to be read together with a
companion paper documenting non-cyclical statistical features
of the same panels (long memory, multifractality, non-linearity,
information complexity, reflexive drift); the companion paper is
in preparation and the present paper will not be submitted for
journal review until the companion is available as a citeable
preprint.

\section*{Reproducibility and open science}

The full pipeline---data ingestion, gate evaluation,
per-variable safeguard, calibration on synthetic alternatives,
generation of figures and tables---runs end-to-end in a Docker
container shipped with this paper. Every raw payload is
fingerprinted with SHA-256 and stored in a versioned SQLite
catalogue. Threshold commitments are recorded as dated Git tags.
The container, data manifests, validation scripts (DOI/ISBN
resolution against the CrossRef API; bibliographic consistency
check \(\{\backslash\)cite\(\}\leftrightarrow\) \texttt{.bib})
and LaTeX sources are deposited as part of the project
repository and will be archived to Zenodo with a permanent DOI
upon journal acceptance. Every numerical result in
Section~\ref{sec:results} and Appendix~\ref{app:per_variable}
comes from a reproducible empirical run; the scripts that
produce them are \path{scripts/calibrate_dual_null.py},
\path{scripts/wen_replication.py},
\path{scripts/boe_kondratieff_per_variable.py},
\path{scripts/jst_per_variable.py},
\path{scripts/wb_per_variable.py} and
\path{scripts/quarterly_per_variable.py}; the outputs they
write are the corresponding \texttt{*\_per\_variable.json}
sidecars under \path{reports/}.

\section*{Acknowledgements}

This work was developed in the EcoWave research project. The
author thanks the contributors to the J\`ord\`a-Schularick-
Taylor Macrohistory Database, the Bank of England's OBRA team,
the Bank for International Settlements and the World Bank Open
Data team for the public availability of the data on which this
study rests. The author is solely responsible for the
methodological choices and for any errors that remain.

\section*{Declaration of competing interests}

The author declares no competing interests.

\section*{Data availability}

All data are derived from public-domain or academically-
licensed sources listed in Appendix~\ref{app:data} with full
provenance, licences and SHA-256 checksums. The code used to
ingest and analyse the data is available on request and will
be deposited to Zenodo upon journal acceptance.
