\section{Data provenance and reproducibility}
\label{app:data}

This appendix documents the five panels of Section~\ref{sec:data} at
the level of detail needed to defend the empirical claim against a
hostile reviewer: source URL, version, access date, SHA-256
checksum, licence, pre-processing decisions, and cross-source
consistency checks. Every panel is reproducible end-to-end inside the
project Docker image.

\subsection{Panel inventory}

\paragraph{World Bank Open Data (WB).}
World Development Indicators \citep{wb_wdi}, annual frequency,
1960--2024, 45 macroeconomic series (real GDP, gross fixed capital
formation, domestic credit, CPI inflation, current-account balance,
\emph{etc.}). Aggregates: WLD (world), HIC (high-income), UMC
(upper-middle-income), LMC (lower-middle-income), LIC
(low-income), G7, and BRICS. Licence: CC~BY~4.0. Access date:
2024-11. SHA-256 of bulk download in
\path{ecowave/db.py:raw_files}.

\paragraph{Quarterly macroeconomic data (Quarterly).}
\citet{bis_credit} for credit-to-GDP and household credit on the
emerging-market and G7 cross-section (Korea, China, Mexico, South
Africa, Turkey, Russia, Indonesia, India, Brazil); FRED \citep{fred},
Eurostat, and OECD for GDP, CPI, ten-year sovereign yields and
unemployment on USA, EA, JPN, GBR plus the G7Q and OECDQ aggregates;
quarterly frequency, 1970--2024, fifteen country-aggregate groups,
fifteen variables. Licence: BIS citation-required, FRED public-
domain, Eurostat and OECD academic-citation. Monthly FRED inputs
are aggregated to quarterly by simple averaging. Real residential
property prices are taken from the BIS property price database
\citep{bis_credit}. Access date: 2024-11.

\paragraph{Jord\`a-Schularick-Taylor R6 (JST).}
\citet{jorda_schularick_taylor2017}, release 6 (2024), annual,
1870--2020, eighteen advanced economies, 45 series including real
GDP, domestic credit, household debt, real house prices, equity
indices, 10-year sovereign yields, and the broad money stock.
Licence: academic citation required. Real-valued nominal series are
deflated by the panel's own CPI. SHA-256 in \path{long_history_manifest.json}.

\paragraph{Bank of England Millennium (BoE Mill.).}
\citet{boe_millennium} OBRA database, annual 1086--2016, with
quarterly coverage from 1700; \(\approx 130\) series (real GDP,
CPI, Bank Rate, unemployment, domestic credit, real GDP per
capita). Splices are documented in the BoE methodology paper and
are propagated verbatim. Licence: citation required.

\paragraph{Sectoral historical panel (Sectoral).}
Eleven historical series (US rail freight ton-miles 1830+, UK pig
iron production 1750+, world coal output 1820+, US/UK cotton and
wheat output 1700+, etc.) drawn from FRED, the UK Department for
Business, Energy \& Industrial Strategy (BEIS), and Our World in
Data (OWID, MIT-licensed). The panel exists specifically to
reproduce \citet{wen2005}'s test on dedicated sectoral series.

\subsection{Pre-processing decisions}

\paragraph{Deflation and log-difference.}
Nominal series are deflated by the relevant price index before
any cycle test. The transformation applied to each variable
(\texttt{log\_diff}, \texttt{level} or \texttt{share\_of\_gdp})
is recorded in the per-panel manifest JSON; the choice is fixed
\emph{ex ante} and does not vary across cycles. The deflators
used are panel-specific:
\begin{itemize}
\item \emph{BoE Millennium 1700--1947 (UK)}: the Bank of
  England OBRA composite CPI of \citet{thomas_dimsdale2017},
  which itself splices the
  \citet{phelps_brown_hopkins1956} cost-of-consumables index
  (1264--1954), the \citet{allen2001} silver-wage
  consumption-basket index, the \citet{clark2005}
  working-class cost-of-living index, and the
  \citet{feinstein1972} retail-price series (1855--1965). The
  splice points are 1750 (Phelps-Brown--Hopkins to Allen),
  1850 (Allen to Clark) and 1900 (Clark to Feinstein); each
  splice is multiplicative on the overlap mean of a five-year
  window.
\item \emph{BoE Millennium 1948--2016 (UK)}: ONS CPI (link to
  CPIH after 2017).
\item \emph{JST R6 (18 economies)}: the panel's own CPI series
  (chain-linked national CPI for each country; see
  \citet{jorda_schularick_taylor2017} release 6 documentation).
\item \emph{WB and Quarterly (multi-country)}: World Bank
  WDI / OECD chain-weighted GDP deflator; FRED series
  \texttt{GDPCTPI} for the US; Eurostat HICP for EA aggregates.
\item \emph{Sectoral (physical quantities)}: no deflation
  required (tons of pig iron, ton-miles of rail freight,
  bushels of wheat).
\end{itemize}

\paragraph{Splicing and gap-filling.}
Splices follow the published methodology of the source (BoE
OBRA, JST R6); the four UK pre-1900 splices are documented
above. Three categories of multi-source splice are used:
\begin{itemize}
\item \emph{Multiplicative splice}: applied to all level series
  (real GDP, CPI, real wages). The scaling factor is the ratio
  of the two sources' means over a five-year overlap window.
\item \emph{Additive splice}: applied to ratio series
  (debt-to-GDP, credit-to-GDP). The shift is the difference of
  the two sources' means over the overlap.
\item \emph{Linear-blend splice}: applied where two sources
  overlap for fewer than five years; a triangular weight
  smoothly transitions from source~A to source~B over the
  overlap.
\end{itemize}
Splice points and methods are recorded in the per-panel
manifest JSON (\path{long_history_manifest.json},
\path{sectoral_history_manifest.json}).

Gaps shorter than two annual or four quarterly periods are
linearly interpolated; longer gaps are left as missing and
excluded from cycle tests on a per-cell basis. Imputation rates
are below 1\,\% on all panels except BoE pre-1700 quarterly,
which is not used in this paper.

\paragraph{National-accounts breaks.}
Three methodological breaks in the underlying national accounts
affect the panels used here: (i) the introduction of the
System of National Accounts (SNA 1953 / SNA 1968 / SNA 1993 /
SNA 2008), (ii) the European System of Accounts revisions
(ESA 1995 \(\to\) ESA 2010), and (iii) the US Bureau of
Economic Analysis 2013 comprehensive revision (which
capitalised R\&D and artistic originals). The JST R6
release~6 (2024) of \citet{jorda_schularick_taylor2017} applies
its own back-revision routine to harmonise pre-2014 series to
the SNA 2008 / ESA 2010 framework; we adopt the JST splice
verbatim. The BoE Millennium series likewise apply the OBRA
back-projection of \citet{thomas_dimsdale2017} to harmonise
pre-1948 to post-1948 conventions; we adopt the OBRA splice
verbatim. For the WB and Quarterly panels we use the
provider's own chained series (WDI chained-linked GDP, FRED
\texttt{GDPC1} chained 2017 dollars), which fold the breaks
into the chain factor.

\paragraph{Pre-1850 caveat: anachronism of ``real GDP''.}
National-accounts measurement is a 1930s--1950s
methodological construct; what is called ``real GDP'' before
1850 on BoE Millennium or in
\citet{deane_cole1962,feinstein1972,maddison1991,mitchell2003ihs}
is a back-projection from sectoral physical quantities (coal,
pig iron, wheat, cotton, rail freight) weighted by
contemporary price relatives. The reconstructed series
inherit the volatility of agricultural output (which
dominates pre-industrial GDP) and the imputation noise of
sectoral weights. Any cycle verdict on real-GDP-style series
in the 1700--1850 window therefore inherits these
limitations; we flag the issue in
Section~\ref{sec:kondratieff_results} where it matters most
(only BoE supports the Kondratieff window).

\paragraph{International comparability and survival bias.}
The five panels are not symmetric in geographic coverage.
The BoE Millennium and the sectoral panel are
UK-and-Anglosphere-dominated. The JST R6 R6 covers eighteen
advanced economies from 1870, but the depth of coverage
before 1914 is much greater for the UK, the US, France and
Germany than for the smaller economies (Norway, Portugal,
Denmark). This is a survivorship bias of the historical
archive: empires and continuously-sovereign states leave
better trails than countries fragmented by occupation or
revolution. France pre-1860, for example, has no continuous
national-accounts series; the \citet{toutain1997}
back-projection is the standard reference but is not yet
spliced into JST R6 R6. The Kondratieff result of
Section~\ref{sec:kondratieff_results} therefore rests on the
UK precisely because the UK has the longest continuous
debt/GDP series in the public-data corpus, not because the
UK is uniquely cyclic.

\paragraph{Z-score normalisation windows.}
Surrogate-bootstrap test statistics use the empirical mean and
variance of the variable on the threshold-transparent window
(committed to the project's Git history before panel ingestion).
Two windows
are reported: 1990--2006 (pre-crisis structural), and 1990--2019
(post-2008 robustness). The verdict is invariant.

\subsection{Cross-source consistency}

To ensure that source-specific quirks do not drive the verdict, we
run the cascade independently on overlapping windows.

\begin{table}[h]
\centering
\caption{Cross-source consistency tests on overlapping windows.
Pass-rate is the fraction of (variable, cycle) cells where the two
sources return the same gate-pass/fail outcome. Pre-registered
tolerance: \(\pm 5\%\).}
\label{tab:cross_source}
\small
\begin{tabularx}{\linewidth}{@{}X l c c@{}}
\toprule
\textbf{Overlap} & \textbf{Period} & \textbf{Pass-rate} & \textbf{In tol.?} \\
\midrule
JST vs.\ BoE (UK)                    & 1870--2016 & 96.3\,\% & \checkmark \\
BIS vs.\ JST (G7 credit)             & 1970--2020 & 95.1\,\% & \checkmark \\
WB vs.\ JST (DE, FR, IT, JP, UK, US) & 1960--2020 & 94.8\,\% & \checkmark \\
\bottomrule
\end{tabularx}
\end{table}

\subsection{Reproducible pipeline}

The full ingestion, gate-evaluation and per-variable safeguard
pipeline is implemented in the EcoWave Python package and runs
end-to-end in \(\approx 30\) minutes inside the Docker container
shipped with this paper (\path{papers/cycles_refuted/Dockerfile}).
The five steps are: (i) build the LaTeX image, (ii) run the unit
tests, (iii) ingest the five panels into a versioned SQLite store
fingerprinted by SHA-256, (iv) run Gates~1--3 with the per-variable
safeguard, (v) consolidate the results into the JSON sidecars that
populate the tables and figures of this paper.

Every result reported in Section~\ref{sec:results} is traceable to
a JSON sidecar in \path{ecowave/reports/} that records the panel,
the variable, the cycle band, the dual-null \(p\)-values, the
consensus vote count, the universality count, and the verdict.
The sidecars conform to the versioned schema \texttt{cycle\_verdict\_v1}.
