\section{Acceptance criteria: full specification}
\label{app:criteria}

This appendix records the protocol thresholds and their
limitations.

\subsection{What ``frozen thresholds'' means here, and what it does not}

The cycle bands, surrogate counts, gate thresholds and safeguard
parameters were committed to the project's public Git history
before any panel was ingested for analysis. The commitment is
verifiable through dated Git tags and the immutable
\texttt{MappingProxyType} export of
\path{ecowave/cycles/bands.py:CYCLE_BANDS}.

We do \emph{not} claim this is a formal pre-registration. Formal
pre-registration as practised on the OSF or AEA RCT registries
requires submission of a complete analysis plan to an
independent third party that timestamps the document outside the
researcher's control. Our commitment is internal to the project
repository: it is auditable but it is auditable by readers, not
by an external registrar. We record the distinction explicitly
because it matters for the interpretation of any negative
result.

The threshold values themselves are anchored to the prior
empirical literature on each cycle, not derived from the data
analysed here. This is the only sense in which the protocol is
``pre-data''.

\subsection{Bands and anchor references}

\begin{center}
\begin{tabularx}{\linewidth}{@{}l c X@{}}
\toprule
\textbf{Cycle} & \textbf{Band (years)} & \textbf{Anchor references} \\
\midrule
Kitchin     & 3--5   & \citet{kitchin1923}; \citet{wen2005}; \citet{diebolt_doliger2008} \\
Juglar      & 7--11  & \citet{juglar1862}; \citet{schumpeter1939} \\
Kuznets     & 15--25 & \citet{kuznets1930}; \citet{korotayev_tsirel2010} \\
Kondratieff & 40--60 & \citet{kondratieff1925}; \citet{modelski1987}; \citet{korotayev_tsirel2010} \\
\bottomrule
\end{tabularx}
\end{center}

\subsection{Gate~1 (existence-plus-coherence)}

At significance \(\alpha=0.05\) on \(B\) AR(1) surrogates per
cell (\(B=1000\) on JST R6, \(B=500\) on Bank of England Millennium
and World Bank, \(B=300\) on the quarterly panel, \(B=200\) on the
sectoral panel; the count is chosen to keep total runtime tractable
on the project's reproducible Docker image), the empirical
band-power must exceed the 95th percentile of the AR(1)-bootstrap
null \emph{and} the within-band Hilbert phase-coherence statistic
must exceed the 95th percentile of the Theiler phase-randomised
null. The two surrogate \(p\)-values \(p_1\) (existence) and
\(p_{\mathrm{coh}}\) (coherence) are recorded separately and
reported in Section~\ref{sec:results}; this acknowledges that the
two surrogates test different aspects of the data
\citep{schreiber_schmitz2000}.

\subsection{Gate~2 (method consensus): dependence of estimators}

A cell passes Gate~\ref{gate:2} iff at least three of four
estimators (Christiano-Fitzgerald, Morlet, Markov-switching,
PELT) concur on the dominant phase at every common time point.
The four estimators are not statistically independent.
On null AR(1) panels (\(\phi=0.5\), \(T=150\), \(N=200\)
replicates), the empirical pairwise phase agreement between
Christiano-Fitzgerald-Hilbert and a Bry-Boschan-style
sign-of-velocity proxy is \(0.79\) (mean; median \(0.79\); see
\path{reports/estimator_pairwise_v1.json} and
\path{scripts/measure_estimator_agreement.py}). This is an
overestimate of inter-method independence for the full four-method
consensus, but it provides the right order of magnitude: the
estimators share enough of the same slope-following structure
that the ``3-of-4'' rule cannot deliver the four-fold
independence factor that would justify a Bonferroni-style
multiplicity argument. We therefore report Benjamini-Hochberg
adjusted \(p\)-values on the full grid of Gate~\ref{gate:1}
tests in Appendix~\ref{app:per_variable} as a complementary
robustness perspective, using the
\path{ecowave.cycles.surrogate.benjamini_hochberg_adjust}
utility shipped with the project.

\paragraph{Pre-registered relaxations.}
Two consensus relaxations are declared in advance and grounded
in sampling constraints: (i) two votes for Kitchin on annual
data, because PELT and Bry-Boschan are under-powered when the
cycle period is fewer than five times the sampling interval;
(ii) two votes for Kondratieff on panels whose window covers
fewer than two full periods (\(< 120\) annual observations),
because Markov-switching and PELT cannot deliver enough state
changes. The relaxations are coded in
\path{ecowave/cycles/consensus.py:RELAX_RULES}.

\subsection{Gate~3 (cross-aggregate concordance): not a universality test}

We count, on the WB income-stratified family (WLD, HIC, UMC,
LMC, LIC), how many aggregates independently pass
Gates~\ref{gate:1}--\ref{gate:2}. We \emph{do not} require
universal concordance: the modern theory of the business cycle
predicts that institutional, monetary and financial differences
across income groups should produce differential cyclical
responses \citep{stock_watson2005}. A cycle that passes on HIC
and UMC but not on LMC or LIC is reported as
``advanced-economy-specific''; this is informative, not
disqualifying.

Verdicts: ``cross-aggregate consistent'' (5/5 or 4/5),
``advanced-economy specific'' (HIC \(\cap\) UMC, others fail),
``regional'' (\(\leq 2/5\)), ``rejected'' (\(0/5\)).

\subsection{Per-variable safeguard: threshold sensitivity}

The threshold of \(0.5\)---the fraction of component variables
required to individually pass Gate~\ref{gate:1} for a composite
to be admitted---is taken from \citet{wen2005}'s usage on
inventory data. We report sensitivity in
Appendix~\ref{app:per_variable}: the qualitative verdict (no
canonical cycle passes the cascade on more than a minority of
panels) is invariant for thresholds in \([0.3, 0.7]\). On panels
with few component variables (BoE Millennium individual UK
series; sectoral 11-series panel) the threshold becomes
mechanical and we discuss the implications in
Appendix~\ref{app:per_variable}.

\subsection{Multiple-comparison correction: BH-FDR as robustness}

We do not apply Bonferroni or Holm correction across the
\(\sim 1\,200\) cells of the grid as a primary verdict because
the cascade itself provides multiplicity protection. However,
because the cascade protection rests on partial independence
assumptions that the empirical correlations of
Section~\ref{sec:methods} only partially satisfy, we report
Benjamini-Hochberg \citep{benjamini_hochberg1995} adjusted
\(p\)-values on the full Gate~\ref{gate:1} grid as a
complementary perspective. The verdict is qualitatively
invariant; the few cells whose status changes are listed in
Appendix~\ref{app:per_variable}.

\subsection{Conditions that would falsify the protocol itself}

The protocol is a conjecture. We declare it falsified on
observation of any of the following:
\begin{enumerate}
\item[(i)] Empirical false-positive rate at Gate~\ref{gate:1} on
  synthetic \(\AR{1}\) panels exceeds \(0.05\) by more than two
  standard errors over \(N=1000\) replicates.
\item[(ii)] Power against Family I synthetic alternatives at
  \(\mathrm{SNR}=1.0\) falls below \(0.80\)
  (Section~\ref{sec:calibration}).
\item[(iii)] Any of the four Gate~\ref{gate:2} estimators fails
  to reproduce its canonical published result on the
  corresponding textbook benchmark.
\end{enumerate}
All three conditions are routinely checked by the project's
test-suite (\path{tests/}). Calibration outputs are in
\path{reports/calibration_v1.json}.
