\section{Per-variable evidence, sensitivity, and FDR-adjusted verdict}
\label{app:per_variable}

This appendix reports the per-variable Gate~\ref{gate:1} evidence
that underpins Section~\ref{sec:results}, with raw \(p\)-values
rather than pass/fail indicators, with sensitivity to the
safeguard threshold and to the analysis window, and with the
Benjamini-Hochberg false-discovery-rate adjusted verdict as a
robustness check.

\subsection{Sectoral panel: empirical \(p\)-values}

Table~\ref{tab:wen_replication_p} reports the AR(1) bootstrap
\(p\)-value \(p_1\) of Gate~\ref{gate:1} for every (variable,
cycle) cell of the sectoral panel, computed by
\path{scripts/wen_replication.py} on the raw data shipped with
the project. The Kondratieff column is empty because no sectoral
series in the panel is long enough to support a meaningful test
on a 40--60y band (we require \(N>4\cdot 60=240\) annual
observations); a dash indicates an untestable band.

\begin{table}[h]
\centering
\caption{Empirical \citet{wen2005} replication on the sectoral
panel. AR(1) bootstrap \(p_1\) on \(B=200\) surrogates per cell,
computed from the raw CSV by
\path{scripts/wen_replication.py}; source:
\path{reports/wen_replication_per_variable.json}. Cells with
\(p_1<0.05\) are shown in bold.}
\label{tab:wen_replication_p}
\small
\begin{tabularx}{\linewidth}{@{}X c c c c@{}}
\toprule
\textbf{Variable (panel period)} & \textbf{Kitchin} & \textbf{Juglar} & \textbf{Kuznets} & \textbf{Kondratieff} \\
\midrule
UK coal output       (1700--2019)  & 0.811 & 0.995 & 0.632 & --- \\
US coal output       (1856--1958)  & 0.224 & 0.811 & 0.726 & --- \\
US cotton            (1912--1961)  & 0.169 & 0.975 & ---   & --- \\
US industrial prod.  (1919--2026)  & 0.174 & 0.224 & 0.881 & --- \\
US rail freight      (1866--1922)  & 0.632 & 0.761 & ---   & --- \\
US steel             (1863--1965)  & 0.766 & 0.189 & ---   & --- \\
US wheat             (1866--1952)  & \textbf{0.040} & 0.592 & ---   & --- \\
US WPI               (1860--2026)  & 0.299 & \textbf{0.015} & 0.701 & --- \\
World coal           (1900--2024)  & 0.299 & 0.672 & \textbf{0.020} & --- \\
World oil            (1900--2024)  & 0.701 & 0.488 & 0.274 & --- \\
\midrule
\textbf{Survival rate at \(\alpha=0.05\)} & 1/10 & 1/10 & 1/6 & 0/0 \\
\textbf{Median \(p_1\)}                   & 0.299 & 0.632 & 0.667 & --- \\
\bottomrule
\end{tabularx}
\end{table}

The unadjusted survival rate is 3 of 26 testable cells at
\(\alpha=0.05\) (US wheat Kitchin, US WPI Juglar, world coal
Kuznets). Under Benjamini-Hochberg adjustment at FDR 0.05
applied to the 26 \(p_1\) values, the critical threshold is
\(p^* = 0.05\cdot 1/26 \approx 0.0019\); none of the three
individually-significant cells passes the BH threshold, so zero
of twenty-six cells survives the FDR-adjusted gate. The three
positive cells under the unadjusted gate are individually
plausible exceptions (US wheat Kitchin: agricultural inventory
cycle; US WPI Juglar: the original Juglar variable; world coal
Kuznets: long-swing residential-construction-style pattern) but
do not constitute evidence for a universal canonical
periodicity. The result reproduces, on real historical data,
the substantive finding of \citet{wen2005}: cycles that appear
on composite aggregates are typically not detectable on the
underlying sectoral series.

\subsection{Sensitivity to the analysis window}

We re-run Gate~\ref{gate:1} on each panel under two robustness
windows. The qualitative verdict on the sectoral panel
(3 unadjusted cells, 0 surviving BH-FDR) is invariant. On JST R6
the Kondratieff band is window-bound (maximum 151 annual
observations per series, below the threshold of 240 required for
a meaningful 40--60y test) and therefore not part of the
window-sensitivity analysis; the JST verdict on the Juglar and
Kuznets bands is invariant to restricting the panel to 1870--2007.
On BoE Millennium, the three unadjusted positives
(UK debt/GDP on Kuznets and Kondratieff, UK unemployment on
Juglar) are stable under restriction to 1700--1945. On the
quarterly panel, the Kitchin and Juglar positives are stable
under restriction to the pre-2007 sub-window. The substantive
concentrations of Section~\ref{sec:results} therefore do not
depend on the inclusion of the post-2008 period.

\subsection{Per-variable Kondratieff on BoE Millennium}

Table~\ref{tab:boe_kondratieff_p} reports the AR(1) bootstrap
\(p_1\) of Gate~\ref{gate:1} for the ten Bank of England
Millennium variables long enough to support a Kondratieff
(40--60y) test (\(N>240\) annual observations). The numbers
come from the raw long-format CSV
(\path{data_raw/boe/annual.csv}) via
\path{scripts/boe_kondratieff_per_variable.py}; source:
\path{reports/boe_per_variable.json}.

\begin{table}[h]
\centering
\caption{Per-variable Kondratieff test on the Bank of England
Millennium panel, 1700--2016. \(p_1\) on \(B=500\) AR(1)
surrogates. Cells with \(p_1<0.05\) shown in bold.}
\label{tab:boe_kondratieff_p}
\small
\begin{tabularx}{\linewidth}{@{}X c c@{}}
\toprule
\textbf{Variable (panel period)} & \(\boldsymbol{p_1}\) & \textbf{Gate~\ref{gate:1}} \\
\midrule
Real GDP (1700--2016)                & 0.643 & rejected \\
Composite real GDP, long (1700--2016)& 0.669 & rejected \\
CPI (1700--2016)                     & 0.615 & rejected \\
Wholesale price index (1700--2016)   & 0.212 & rejected \\
Bank Rate (1700--2016)               & 0.778 & rejected \\
Consols long-term yield (1703--2016) & 0.102 & rejected \\
Public debt / GDP (1700--2016)       & \textbf{0.004} & \textbf{passes} \\
Share prices (1700--2016)            & 0.986 & rejected \\
Population GB/NI (1700--2016)        & 0.291 & rejected \\
Unemployment rate (1760--2016)       & 0.088 & rejected \\
\midrule
\textbf{Survival rate at \(\alpha=0.05\)} & \multicolumn{2}{r}{1/10} \\
\bottomrule
\end{tabularx}
\end{table}

One of ten Kondratieff-eligible BoE variables passes
Gate~\ref{gate:1} at the unadjusted significance level: the
public-debt-to-GDP ratio, with \(p_1=0.004\). This is the
canonical Reinhart-Rogoff long-debt-cycle signature, driven on
UK data by the Napoleonic, Crimean and two World Wars financing
peaks. The same variable also passes the Kuznets band
(\(p_1=0.006\)). Both passings are consistent with prior
literature on UK fiscal cycles
\citep{reinhart_rogoff2009} and are properly understood as
\emph{debt-financing} cycles tied to exogenous war shocks, not
as evidence for the existence of a universal endogenous 40--60y
periodicity.

Across the full BoE Gate~\ref{gate:1} run (16 variables \(\times\)
4 cycle bands, 58 testable cells), three cells pass unadjusted:
public debt / GDP on Kuznets (\(p_1=0.006\)) and Kondratieff
(\(p_1=0.004\)), and the unemployment rate on Juglar
(\(p_1=0.006\)). Under Benjamini-Hochberg adjustment at FDR
0.05 (critical threshold \(p^* = 0.05/58 \approx 0.00086\)),
none of the three survives. The expected number of unadjusted
positives under the joint null is 2.9; observing three is
consistent with sampling noise. The unadjusted positives are
nonetheless interesting individually and are flagged for the
substantive literature, but they do not constitute evidence for
the strong universalist reading of any canonical cycle.

\subsection{Per-variable Juglar and Kuznets on Jord\`a-Schularick-Taylor R6}

We apply Gate~\ref{gate:1} to every (country, variable, cycle)
cell of the JST R6 panel for which the panel window admits a
meaningful test (\(N > 4 \cdot \text{hi\_years}\)). The
Kondratieff band cannot be evaluated on JST: the maximum window
1870--2020 yields at most 151 annual observations per series,
short of our threshold \(4\cdot 60=240\). The Kondratieff
verdict on the longest panels therefore rests on BoE Millennium
alone. The script that produces the numbers below is
\path{scripts/jst_per_variable.py}; source:
\path{reports/jst_per_variable_b1000.json} (\(B=1000\) surrogates).

\paragraph{Juglar (605 testable cells).}
67 cells pass Gate~\ref{gate:1} at the unadjusted significance
level (11.1\%), against an expectation of approximately 30
under the joint null at \(\alpha=0.05\)---a 2.2-fold excess.
The distribution of the positives across variables is
substantively informative: \texttt{LH\_XRUSD} (bilateral USD
exchange rate) passes on 11 of 18 countries (61\,\%);
\texttt{LH\_INV} (investment/GDP) on 7 of 18 (39\,\%);
\texttt{LH\_UNRATE} on 6 of 18 (33\,\%);
\texttt{LH\_BUSCREDIT} on 5 of 15 (33\,\%); and
\texttt{LH\_RCONS}, \texttt{LH\_HPI},
\texttt{LH\_RGDP\_BARRO}, \texttt{LH\_DEBTGDP} on 4 each.
The smallest \(p_1\) (\(=0.001\), the surrogate floor at
\(B=1000\)) is observed on investment in Switzerland and Canada
and on unemployment in Portugal.

\paragraph{Kuznets (529 testable cells).}
51 cells pass Gate~\ref{gate:1} at the unadjusted significance
level (9.6\%), against an expectation of \(\sim 26\)---a
1.9-fold excess. \texttt{LH\_HPI} (house prices) passes on
\textbf{6 of 13 countries (46\,\%)}; \texttt{LH\_POP}
(population) on 7 of 18 (39\,\%); \texttt{LH\_CREDIT} (total
loans) on 7 of 17 (41\,\%); \texttt{LH\_MORT} on 5;
\texttt{LH\_DEBTGDP} and \texttt{LH\_CA} on 4. The smallest
\(p_1\) (\(=0.001\)) is observed on population in Belgium and
Portugal and on house prices in the Netherlands and the USA.

\paragraph{Benjamini-Hochberg adjustment on the JST grid.}
Across the full 1\,134-cell JST grid (Juglar + Kuznets), the
BH-FDR critical threshold at \(\alpha=0.05\) is
\(p^* = 0.05 / 1134 \approx 4.4 \cdot 10^{-5}\). With \(B=1000\)
surrogates, no individual cell can attain a \(p_1\) below the
surrogate floor \(1/(B+1) \approx 1 \cdot 10^{-3}\), which is
itself one order of magnitude above \(p^*\). The 118
unadjusted positives therefore all fail BH adjustment in the
present run; whether some of them would survive at
\(B \geq 10\,000\) is an open empirical question, and the
\path{scripts/jst_per_variable.py} script supports such a run.

\paragraph{Interpretation.}
The unadjusted JST positives are substantively interesting and
not noise: they concentrate exactly where the canonical
literature predicts they should (investment for Juglar; housing,
demographics and credit for Kuznets). They do not, however,
amount to a universal canonical cycle in the strong sense: the
fraction of cells passing is small (10\,\%), the concentration
is variable-specific rather than universal across the macro
grid, and Benjamini-Hochberg correction at FDR 0.05 erases the
collective claim. The JST evidence is consistent with the
substantive theory of Juglar (investment-financed cycles) and
Kuznets (construction swings) but inconsistent with a strong
universalist sinusoidal reading on every variable.

\subsection{Sensitivity to the safeguard threshold}

For thresholds in \(\{0.3, 0.5, 0.7\}\), the qualitative
verdict on every panel is invariant. The only cell whose
status depends on the threshold is the WB world Kitchin composite
(rejected at any threshold \(\geq 0.3\) under the safeguard;
admitted only if no safeguard is applied). We retain
\(0.5\) as the primary value following \citet{wen2005}'s usage.

\subsection{Long-memory and stationarity diagnostics}
\label{sec:appendix_long_memory}

Following the R1 referee recommendation, we report on every cell
the four pre-cycle diagnostics introduced in
Appendix~\ref{sec:longmem_diagnostics}: ADF
\citep{dickey_fuller1979}, KPSS \citep{kpss1992}, GPH
fractional-integration order \(\hat d\)
\citep{geweke_porter_hudak1983} and DFA Hurst exponent
\(\hat H\) \citep{peng1994}. The script is
\path{scripts/long_memory_diagnostics.py}; sidecar:
\path{reports/long_memory_diagnostics.json}. Diagnostics are
computed on the input series as ingested (without the
\texttt{log\_diff}/\texttt{share\_of\_gdp} transformation that
Gate~1 applies subsequently), to characterise the
raw long-memory profile of each variable.

\begin{table}[h]
\centering
\caption{Long-memory and stationarity diagnostics on the raw
input series. ADF non-rejection signals a unit root; KPSS
rejection signals departure from stationarity; \(|\hat d|>0.1\)
or \(\hat H>0.6\) signal long memory beyond AR(1). Numbers come
from \path{reports/long_memory_diagnostics.json}.}
\label{tab:longmem_summary}
\small
\begin{tabularx}{\linewidth}{@{}X r r r r@{}}
\toprule
\textbf{Diagnostic} & \textbf{JST R6 (611 cells)} & \textbf{BoE (65 cells)} \\
\midrule
Median \(\hat d_{\mathrm{GPH}}\)               & +0.490 & +0.490 \\
\(|\hat d|>0.1\) (share)                       & 97\,\% & 100\,\% \\
\(|\hat d|>0.4\) (share)                       & 88\,\% & 95\,\% \\
Median \(\hat H_{\mathrm{DFA}}\)               & 1.76   & 1.64 \\
\(\hat H>0.6\) (share)                         & 97\,\% & 94\,\% \\
\(\hat H>1.0\) (share)                         & 88\,\% & 92\,\% \\
ADF unit-root not rejected at \(\alpha=0.05\)  & 81\,\% & 83\,\% \\
KPSS stationarity rejected at \(\alpha=0.05\)  & 77\,\% & 89\,\% \\
\bottomrule
\end{tabularx}
\end{table}

\paragraph{Implication.}
On both panels the raw input series exhibit substantial
long-memory and near-unit-root behaviour: median \(\hat
H\geq 1.6\) (consistent with I(1) random-walk-like dynamics on
level series), \(|\hat d|\) saturated at the GPH clipping bound
of 0.49 on the majority of cells, and ADF unable to reject the
unit-root null on roughly four cells in five. An AR(1) null
fitted on the raw level is therefore mis-specified for the
majority of cells. Gate~1 in practice operates on the
post-transformation series (\texttt{log\_diff} for most level
series, \texttt{share\_of\_gdp} for ratios); after
log-differencing the persistence reduces materially. The
honest reading is nonetheless that the AR(1) Gate~1 verdict
should be cross-validated against the ARFIMA(0,\(\hat
d\),0) Gate~1 verdict reported by
\path{scripts/arfima_null_per_cell.py} (sidecar
\path{reports/arfima_null_per_cell.json}). Cells that pass
under both nulls gain credibility; cells that pass only the
AR(1) null and fail the ARFIMA null should be downgraded as
candidates for the variable-specific vindication claim.

\subsection{Band-edge sensitivity}
\label{sec:appendix_band_sensitivity}

Following the R4 recommendation, we rerun Gate~1 with the
canonical bands perturbed on each edge by \(\pm 1\)y
(Kitchin/Juglar) or \(\pm 2\)y (Kuznets/Kondratieff), plus
widen/narrow variants. Script:
\path{scripts/band_sensitivity.py}; sidecar:
\path{reports/band_sensitivity.json}. A substantive cycle
should remain detected when the band is perturbed by one
year; a band-fitting artefact will not.
Table~\ref{tab:band_sensitivity_boe} reports the BoE
Millennium pass-rates (1541 cells, \(B=300\) surrogates,
65 variables, 27 cycle\(\times\)perturbation aggregates).

\begin{table}[h]
\centering
\caption{Band-edge sensitivity of Gate~1 on BoE Millennium.
Pass-rate by (cycle, perturbation). ``anchor'' is the
literature-anchored band. Perturbations move one edge in
or out by \(\pm 1\)y (Kitchin/Juglar) or \(\pm 2\)y
(Kuznets/Kondratieff); ``narrow'' and ``widen'' move both
edges simultaneously. Source:
\path{reports/band_sensitivity.json}.}
\label{tab:band_sensitivity_boe}
\small
\begin{tabularx}{\linewidth}{@{}X c c c c c c c@{}}
\toprule
\textbf{Cycle} & \textbf{anchor} & \textbf{tighten lo} & \textbf{loosen lo} & \textbf{tighten hi} & \textbf{loosen hi} & \textbf{narrow} & \textbf{widen} \\
\midrule
Juglar [7,11]      & 15.4\,\% & 10.8\,\% & 12.3\,\% & 15.4\,\% &  9.2\,\% & 13.8\,\% & 10.8\,\% \\
Kuznets [15,25]    & 12.9\,\% & 11.3\,\% & 14.5\,\% & 10.9\,\% & 11.3\,\% &  9.4\,\% & 12.9\,\% \\
Kondratieff [40,60] & 10.5\,\% &  7.9\,\% & 10.5\,\% & 13.2\,\% & 11.8\,\% & 13.2\,\% & 14.7\,\% \\
Kitchin [3,5]      &  7.7\,\% &  9.2\,\% &  \textbf{0.0\,\%} &  4.6\,\% & \textbf{16.9\,\%} &  4.6\,\% &  4.6\,\% \\
\bottomrule
\end{tabularx}
\end{table}

\paragraph{Interpretation.}
Three of the four cycles are stable to band-edge
perturbation: Kuznets (9.4--14.5\,\%), Kondratieff
(7.9--14.7\,\%) and Juglar (9.2--15.4\,\%) span a range of
at most six percentage points around the anchor pass-rate.
\textbf{Kitchin is the exception}: tightening the lower
edge to [4,5] yields a zero pass-rate, while loosening the
upper edge to [3,6] more than doubles the pass-rate to
16.9\,\%. The asymmetric sensitivity is exactly the
signature of a band-fitting artefact: the substantive signal
on BoE within a [3,5] window does not survive a one-year
perturbation in either direction. This vindicates the R4
critique on the Kitchin cell of BoE specifically, and we
discount the BoE Kitchin headline accordingly in
Section~\ref{sec:kitchin_results}. The JST and quarterly
panels, which carry the load-bearing Kitchin claims of the
paper, should be re-run with the same sensitivity script
before any Kitchin-specific revision; the BoE Kitchin signal
is no longer treated as supporting evidence.

\subsection{Rolling-window Gate~1: temporal stability}
\label{sec:appendix_rolling}

Following the R5 recommendation, we report Gate~1 verdicts on
a grid of rolling windows of fixed length (80y for the
Kondratieff window-bound cells; 50y for Kitchin/Juglar/Kuznets;
step 40y on annual panels). Script:
\path{scripts/rolling_window_gates.py}; sidecar:
\path{reports/rolling_window_gates.json}. On the BoE
Millennium 1700--2016 the run produces 1\,646 rolling cells
across 65 variables; aggregate pass-rates per cycle are:

\begin{itemize}
\item Juglar: 57 / 466 windows pass Gate~1 (12.2\,\%)
\item Kitchin: 40 / 466 (8.6\,\%)
\item Kuznets: 39 / 430 (9.1\,\%)
\item Kondratieff: 40 / 284 (14.1\,\%)
\end{itemize}

These rates are modestly elevated above the 5\,\% nominal null
but compatible with intermittent presence rather than
stationary cyclicality across the full 1700--2016 horizon. A
substantive cycle that lives in one epoch but is absent in
another (e.g.\ Belle \'Epoque vs Trente Glorieuses vs
post-2008) is not detected by a single full-window test; the
heat-map shipped in the JSON sidecar resolves the
epoch-by-epoch presence.

\subsection{ARFIMA-vs-AR(1) Gate~1 on BoE Millennium}
\label{sec:appendix_arfima_vs_ar1}

Following the R1 recommendation, we rerun Gate~1 on every
BoE cell with the AR(1) null replaced by an ARFIMA(0,
\(\hat d_{\mathrm{GPH}}\), 0) null. The cross-tabulation of
the two verdicts is the empirical test of whether the AR(1)
positives survive long-memory-aware re-evaluation. Script:
\path{scripts/arfima_null_per_cell.py}; sidecar:
\path{reports/arfima_null_per_cell.json}; on BoE (230 cells
total across the four cycles, \(B=500\)).

\begin{table}[h]
\centering
\caption{Cross-tabulation of Gate~1 verdicts under AR(1)
versus ARFIMA(0, \(\hat d\), 0) nulls on the BoE Millennium
panel.}
\label{tab:arfima_vs_ar1_boe}
\small
\begin{tabularx}{\linewidth}{@{}X r r r r r@{}}
\toprule
\textbf{Cycle} & \textbf{n} & \textbf{AR(1) pass} & \textbf{ARFIMA pass} & \textbf{both} & \textbf{only AR(1)} \\
\midrule
Kitchin       & 65 & 5 & 1 & 1 & 4 \\
Juglar        & 65 & 8 & 4 & 2 & 6 \\
Kuznets       & 62 & 8 & 9 & 4 & 4 \\
Kondratieff   & 38 & 5 & 6 & 3 & 2 \\
\bottomrule
\end{tabularx}
\end{table}

\paragraph{Interpretation.}
Ten cells pass \emph{both} the AR(1) and the ARFIMA null on
BoE; they are the long-memory-robust subset of the BoE
positives. Among these survivors the substantive
headlines remain intact: \textbf{UK unemployment on Juglar}
(\(p_{1,\mathrm{AR(1)}}=0.004\), \(p_{1,\mathrm{ARFIMA}}=0.002\)),
\textbf{UK central-government gross debt on Kondratieff}
(\(p_{1,\mathrm{AR(1)}}=0.032\),
\(p_{1,\mathrm{ARFIMA}}=0.048\)), \textbf{UK public-sector
debt on Kondratieff}
(\(p_{1,\mathrm{AR(1)}}=0.002\),
\(p_{1,\mathrm{ARFIMA}}=0.022\), \(\hat d=+0.436\)),
\textbf{real USD-GBP exchange rate on Juglar},
\textbf{real-eri and nominal-eri on Kuznets}. The
\textbf{Kondratieff debt-chronology reading of
Section~\ref{sec:kondratieff_results} is reinforced}, not
overturned, by the ARFIMA-conditional verdict: the headline
\(p_1\) value remains below 0.05 under both nulls, with a
GPH-estimated \(\hat d\) at the long-memory clipping bound
(0.44--0.47) that confirms the series is fractionally
integrated. The 16 cells that pass only the AR(1) null and
fail the ARFIMA null are downgraded as candidates for the
variable-specific vindication claim.
